SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-11 docs/questioning.tex
more on conclusions
small fixes and additions in VI

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering (i.e., phishing ---
{\it transition}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays user input
without appropriate validation. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database ({\it transition}: {\sc dsl} 1 \text{\textbar}
{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
Note that an {\sc xss} attack can start from both routes.

@@

Moreover, extensive accuracy tests may lead to more
well-designed and robust mechanisms. Observe that mechanisms
that can be circumvented were not extensively tested
in terms of accuracy. For instance, {\sc didafit}
was not tested at all and {\sc xss-guard}'s testing involved
6 known attacks. This also applies to some frameworks coming
from the taint tracking subcategory.
Perhaps with more tests the authors would design
their mechanisms differently.

Limiting the scope of the attacks to
be detected may lead to an efficient tool.
Consider the system by Stock et al. It is the only one
that targets exclusively {\sc dom}-based
{\sc xss} attacks and detects them in an accurate manner
as seen in Table~\ref{tab:comp}. Notice also
its extensive testing in real-world attacks.

>>>>

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering (i.e., phishing ---
{\it transition}: {\sc p-xss} 1.1 \text{\textbar} {\sc n-xss} 1.1 \text{\textbar} {\sc csrf} 1).
Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays user input
without appropriate validation. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database ({\it transition}: {\sc dsl} 1 \text{\textbar}
{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
Note that an {\sc xss} attack can start from both routes.

@@

Apart from demonstrating the value of a mechanism, good accuracy tests
may be beneficial per se, by leading to more well-designed and robust
mechanisms. Mechanisms that can be circumvented were not extensively
tested in terms of accuracy. For instance, {\sc didafit} was not
tested at all and {\sc xss-guard}'s testing involved 6 known attacks.
This also applies to some frameworks coming from the taint tracking
subcategory. It is possible that more tests during development would
have led the authors to wider improvements in design. 
%% PL: Do we have a reference in Software Engineering correlating
%% testing with better design?

The accuracy of a tool may be related to the scope of the attacks it
aims to detect. A more limited scope may allow the development of more
accurate tools. In this vein, the system by Stock et al~\cite{SLMS14}
is the only one that targets exclusively {\sc dom}-based {\sc xss}
attacks and detects them in an accurate manner as seen in
Table~\ref{tab:comp}. It is also extensively tested in real-world
attacks.

Apart from testing practices, another area that merits improvement is
the availability of source code and testbeds. We are not aware of
specific reasons why authors of attack detection mechanisms seem to be
wary of releasing online their code and tests. Our finding may reflect
the status in the current point in time, when authors are urged to
publish their code and tests, and may start, or may have already
started doing so, but this does not show yet in the research we
examined, which goes several years back. We also saw instances where
material was published, but does not seem to be available any more.
That points to the importance of curation of research materials. That
is a problem arising in all scientific fields. It is not enough to
publish the underlying code and data, but to make sure that it remains
accessible and to provide the means to test it even as technology
progresses and operating systems, file formats, and software libraries
change. That may be too much to ask right now; what seems reasonable,
though, is to ask of researchers in attack detection mechanisms not to
buck the trend and to take steps to increase the availability of their
research.
